Clean and Process Raw Data

### 2019-07-31 data-raw/README.Rmd
Update data-raw README

```{r libraries}
library(tidyverse)
library(agricolae)
library(usethis)
```

@@

```{r 2015Exp}
files <-
  list.files("data", pattern = "^DS2015_Raw", full.names = TRUE)

@@

# Add days after inoculation column
DS2015 <- 
  DS2015 %>%
  mutate(
    DAI = case_when(
      ASMT == 1 ~ 14,
      ASMT == 2 ~ 22,
      ASMT == 3 ~ 35,
      ASMT == 4 ~ 49,
      ASMT == 5 ~ 62,
    )
  )

@@

# Arrange columns --------------------------------------------------------------
DS2015 <-
  DS2015 %>% select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  )

@@

rm(files, reformat)

```

@@

```{r}
# Preprocess 2016 data for all assessments
#
# 1. Cleanup date format and fill empty dates
# 2. Fill empty NTIL (for same hill, not missing values)
# 3. Fill empty NTShB (for same hill, not missing values)
# 4. Add column with number of days after inoculation (DAI)

@@

DS2016 <- as_tibble(arrange(DS2016, ASMT, PLOT))

@@

RAW_data <- as_tibble(rbind(as.data.frame(DS2015),
                                    as.data.frame(DS2016)))

# convert columns to factor ----------------------------------------------------
RAW_data$YEAR <- factor(RAW_data$YEAR)
RAW_data$ASMT <- factor(RAW_data$ASMT)
RAW_data$PLOT <- factor(RAW_data$PLOT)
RAW_data$REP <- factor(RAW_data$REP)
RAW_data$TRT <- factor(RAW_data$TRT)
RAW_data$WMGT <- factor(RAW_data$WMGT)
RAW_data$NRTE <- factor(RAW_data$NRTE)
RAW_data$SMPL <- factor(RAW_data$SMPL)
RAW_data$HILL <- factor(RAW_data$HILL)
RAW_data$TIL <- factor(RAW_data$TIL)
RAW_data$LEAF <- factor(RAW_data$LEAF)

@@

@@

# add column with midpoint +1  % leaf ShB severity -----------------------------
RAW_data <-
  mutate(
    RAW_data,
    PERC_LEAF_ShB = case_when(
      LEAF_ShB == 0 ~ 1,
      LEAF_ShB == 1 ~ 2.5,
      LEAF_ShB == 2 ~ 10,
      LEAF_ShB == 3 ~ 32.5,
      LEAF_ShB == 4 ~ 75,
      TRUE ~ 100
    )
  )

@@

```{r DSI}
TShB_sev_15 <- 
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
  arrange(PLOT) %>% 
  mutate(DSI = PERC_TIL_ShB + ())
```

@@

# 2015 Tiller incidence AUDPS --------------------------------------------------
TShb_inc_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(
    .funs = funs(mean(., na.rm = TRUE)),
    .vars = vars(PLOT_TShB_incidence = TShB_incidence)
  ) %>%
  arrange(PLOT) %>%
  group_by(YEAR, REP, TRT, PLOT) %>%
  summarise(AUDPS = audps(PLOT_TShB_incidence, DAYS))

# 2015 Tiller Severity AUDPS ---------------------------------------------------
TShB_sev_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
  arrange(PLOT)

@@

# Calculate 2015 AUDPS ---------------------------------------------------------

TShB_inc_AUDPS <-
  audps(evaluation = TShB_inc_wide[, 2:6],
                   dates = pull(TShB_inc_15[1:5, 6]))

>>>>

```{r libraries}
library(tidyverse)
library(agricolae)
library(usethis)
library(lubridate)
```

@@

```{r 2015Exp}
# Preprocess 2015 data for all assessment dates

files <-
  list.files("data", pattern = "^DS2015_Raw", full.names = TRUE)

@@

# Add days after inoculation column
DS2015 <-
  DS2015 %>%
  mutate(DAI = case_when(ASMT == 1 ~ 14,
                         ASMT == 2 ~ 22,
                         ASMT == 3 ~ 35,
                         ASMT == 4 ~ 49,
                         ASMT == 5 ~ 62))

@@

# Arrange columns --------------------------------------------------------------
DS2015 <-
  DS2015 %>% select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  ) %>% 
  mutate(REP = as.integer(REP),
         HILL = as.integer(HILL))

@@

rm(files, reformat)
```

@@

 Preprocess 2016 data for all assessments

1. Cleanup date format and fill empty dates
2. Fill empty NTIL (for same hill, not missing values)
3. Fill empty NTShB (for same hill, not missing values)
4. Add column with number of days after inoculation (DAI)

```{r}
library(tidyverse)
library(agricolae)
library(usethis)
library(lubridate)

@@

DS2016 <- arrange(DS2016, ASMT, PLOT)

@@

RAW_data <- bind_rows(DS2015, DS2016)

# convert columns to factor ----------------------------------------------------
RAW_data <-
  RAW_data %>%
  mutate(
    YEAR = as.factor(YEAR),
    ASMT = as.factor(ASMT),
    PLOT = as.factor(PLOT),
    REP = as.factor(REP),
    TRT = as.factor(TRT),
    WMGT = as.factor(WMGT),
    NRTE = as.factor(NRTE),
    SMPL = as.factor(SMPL),
    HILL = as.factor(HILL),
    TIL = as.factor(TIL),
    LEAF = as.factor(LEAF)
  )

@@

# add column with midpoint +1  % tiller ShB severity ---------------------------

RAW_data <-
  mutate(
    RAW_data,
    PERC_TIL_ShB_1 = case_when(
      TIL_ShB == 0 ~ 1,
      TIL_ShB == 1 ~ 2.5,
      TIL_ShB == 2 ~ 10,
      TIL_ShB == 3 ~ 32.5,
      TIL_ShB == 4 ~ 75,
      TRUE ~ 100
    )
  )

@@

# add column with midpoint +1  % leaf ShB severity -----------------------------
RAW_data <-
  mutate(
    RAW_data,
    PERC_LEAF_ShB_1 = case_when(
      LEAF_ShB == 0 ~ 1,
      LEAF_ShB == 1 ~ 2.5,
      LEAF_ShB == 2 ~ 10,
      LEAF_ShB == 3 ~ 32.5,
      LEAF_ShB == 4 ~ 75,
      TRUE ~ 100
    )
  )

@@

```{r DSI}
#DS2015 <- 
#  DS2015 %>% 
#  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>% 
#  mutate(TShB_DSI = (TIL_ShB + )/
```

@@

TShB_sev_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
  arrange(PLOT)

@@

TShb_inc_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
               .vars = vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  arrange(PLOT) %>%
  group_by(YEAR, REP, TRT, PLOT) %>%
  summarise(AUDPS = audps(PLOT_TShB_incidence, DAYS))
